---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.
-->

```{r development-2}
# Run all this chunk in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))

# Example dataset
file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows
datafile <- system.file("nyc_squirrels_sample.csv", package = "addrsheff")
nyc_squirrels <- read.csv(datafile)

nyc_squirrels
```


# The first function of the package: Calculate the median of a vector

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead

After inflating the template

-  This function code will be added in a new file in the "R/" directory
-->

```{r function}
#' My median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will be added in the '@examples' part of our function above in the "R/" directory
- This example will be added in the vignette created from this Rmd template
-->

```{r examples}
my_median(1:12)
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will be added in the "tests/testthat/" directory
-->

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})
```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

## Use sub-functions in the same chunk

```{r function-my_other_median}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-my_other_median}
my_other_median(1:12)
```

```{r tests-my_other_median}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

## Add postcode variables

```{r function-add_postcode_vars}
#' Add postcode variables e.g. Ward, to a data frame with postcodes  
#'
#' @param df data frame with a postcode variable
#' @param pcd_name name of the postcode variable in passed the data frame
#' @param .admin_district boolean indicating whether to add an admin_district variable
#' @param .lat_long boolean indicating whether to add a pair of latitude & longitude variables
#' @param other_vars character vector of other variables to add
#'
#' @return
#' data frame with variables added based on postcode
#' @export
#'
#' @examples
add_postcode_vars <- function(df, 
                              pcd_name = "postcode",
                              .admin_district = TRUE,
                              .lat_long = FALSE,
                              other_vars = character(0)){
  
  # library(tidyverse) 
  # library(PostcodesioR)
  # library(magrittr)

  ## bulk_postcode_lookup() is currently not ignoring white space ----
  # - looks like it might be a postcodes.io issue rather than PostcodesioR
  
  # New variable with postcode minus white space
  df <- dplyr::mutate(
    df, 
    postcode_query = stringr::str_replace_all(postcode, " " , "")
  )
  
  ## Build a vector of variables of interest ----
  
  # Create an empty character vector  
  pcd_vars <- character(0)
  
  # From the arguments passed in the function call
  if(.admin_district) pcd_vars <- append(pcd_vars, "admin_district")   
  
  if(.lat_long) pcd_vars <- append(pcd_vars, c("longitude", "latitude"))
  
  if(length(other_vars) > 0) pcd_vars <- append(pcd_vars, other_vars) 
  
  # Remove any duplicates
  pcd_vars <- unique(pcd_vars)
  
  ## Build a postcode lookup template and a list of columns in the template ----
  
  # Empty postcode lookup data frame template
  pcd_template <- PostcodesioR::postcode_lookup("S1 2HH") %>%
    dplyr::filter(postcode == "ZZ ZZZ")
  
  # Data frame of postcode lookup column names, types & indices
  pcd_cols <- tidyr::tibble(
    name = colnames(pcd_template), 
    type = lapply(pcd_template, class)) %>% #TODO: lose or use & extract from list
    tibble::rowid_to_column(var = "rowid") %>% 
    dplyr::relocate(rowid, .after = last_col()) 
  
  # The position of "codes" helps with nested "*_code" values
  min_codes_var <- pcd_cols %>% 
    dplyr::filter(stringr::str_ends(name, "_code")) %>% 
    dplyr::filter(rowid == min(rowid))
  
  codes_position <- min_codes_var$rowid
  
  # Add index used to extract var from results
  pcd_cols <- dplyr::mutate(
    pcd_cols, index = purrr::map(
      rowid,
      ~ ifelse(.x < codes_position,
        list(c(2, .x)),
        list(c(
          2,
          codes_position,
          .x + 1 - codes_position
        ))
      )
    )) %>%
    dplyr::select(-rowid)
  
  # Filter list of postcode columns to vars of interest
  pcd_cols <- dplyr::filter(pcd_cols, name %in% pcd_vars)
  
  # Filter template columns to vars of interest
  pcd_details <- dplyr::select(pcd_template, dplyr::all_of(pcd_vars)) %>% 
    dplyr::mutate(postcode_query = as.character())
    
  
  # Need to distinguish between postcode passed & matched e.g. s1 2hh & S1 2HH
  pcd_match <- "postcode" %in% colnames(pcd_details) # flag is used more than once 
  
  if(pcd_match) pcd_details <- pcd_details %>% 
    dplyr::mutate(pcd_match = character(0)) 
  
  ## Do some checks -----
  
  # Check we have some postcode variables in the function arguments
  stopifnot(length(pcd_vars) > 0) 
  
  # Check we have some VALID postcode variables in the function arguments
  stopifnot(nrow(dplyr::filter(pcd_cols, name %in% pcd_vars)) > 0) 
  
  # Warn if there's an unused postcode variable from the function arguments
  if(length(pcd_vars)!=length(pcd_cols)) {
    warnings(paste0(
      "One or more of the variables requested is not available. ",
      "Check spelling and docs.ropensci.org/PostcodesioR/")
    )
  }
  
  ## Handle empty & duplicate postcodes -----
  
  # Snapshot to refer and join to later 
  df_orig <- df
  
  # PostcodesioR expects postcodes to be labelled "postcode" 
  df <- dplyr::rename(df, postcode = {{pcd_name}}) # we rename it back in the returned df
  
  # Don't process empty or duplicate postcodes  
  df <- df %>% 
    tidyr::drop_na(postcode) %>% 
    dplyr::distinct(postcode, .keep_all = TRUE)
  
  ## Batch-by-batch postcode lookup ----
  
  # PostcodesioR puts 100 row limit on bulk_postcode_lookup
  #  - so we're going to have to process the request in batches
  batch_size_max <- 100
  
  ### Batch loop prep ----
  
  # Numbers involved in breaking postcode lookup into batches
  total_rows <- nrow(df)
  
  whole_batches <- total_rows %/% batch_size_max
  
  remainder_batch_size <- total_rows %% batch_size_max
  
  n_batches <- ifelse(remainder_batch_size == 0, whole_batches, whole_batches + 1)
  
  ### Batch loop ----
  for (i in 1:n_batches) {
    
    #### Slice a batch ----
    
    # Determine the size of the batch
    batch_size <- ifelse(i != n_batches, batch_size_max, remainder_batch_size)
    
    # Small probability (1 in 100) but need to check ...
    batch_size <- ifelse(batch_size == 0, batch_size_max, batch_size)
    
    # Determine the start and end records of the batch
    batch_start <- ifelse(i == 1, 1, ((i-1) * batch_size_max) + 1)
    
    batch_end <- ifelse(
      i == n_batches,
      (ifelse(i == 1, i, (i - 1)) * batch_size_max) + remainder_batch_size,
      i * batch_size_max
    )
    
    # Get a batch of petition records
    batch <- dplyr::slice(df, batch_start:batch_end)
    
    #### Bulk lookup request to postcodes.io ----
    bulk_lookup_rslt <- PostcodesioR::bulk_postcode_lookup(
      list(postcodes = batch$postcode_query)
    )
    
    #### Extract the vars from the postcodes.io results in to a data frame ----
    df_batch_rslt <- purrr::map2_dfc(
      pcd_cols$name, 
      pcd_cols$index,
      ~ dplyr::tibble(!!.x := purrr::map(
          bulk_lookup_rslt,
          unlist(.y),
          .default = NA)
          )
      ) %>%
      tidyr::unnest(cols = dplyr::all_of(pcd_vars))
    
    # Need to distinguish between postcode passed & matched e.g. s1 2hh & S1 2HH
    if(pcd_match) df_batch_rslt <- df_batch_result %>% 
      dplyr::rename(pcd_match = postcode) 
    
    # Add postcode passed i.e. our primary key
    df_batch_rslt <- tibble::add_column(
      df_batch_rslt,  
      postcode_query = purrr::map_chr(bulk_lookup_rslt, c(1, 1), .default = ""),
      .before = 1
    )
    
    # Cumulative results from batches
    pcd_details <- dplyr::bind_rows(pcd_details, df_batch_rslt)
  }
  
  # Add postcode variables of interest to the original data
  df_new  <- df_orig %>%
    dplyr::left_join(pcd_details, by = c("postcode_query")) %>% 
    dplyr::select(-postcode_query)
}
```

```{r examples-add_postcode_vars}
# Create a data frame with some example records
# GH Action
df <- tibble::tribble(
  ~name,    ~postcode,
  "SCC",    "S1 2HH",
  "Blades", "S2 4SU",
  "Owls",   "S6 1SW"
)

add_postcode_vars(
  df,
  pcd_name = "postcode",
  .admin_district = FALSE,
  .lat_long = TRUE,
  other_vars = c("admin_ward", "msoa_code")
)
```

```{r tests-add_postcode_vars}
# test_that("add_postcode_vars works properly and show error if needed", {
#   expect_true(add_postcode_vars(1:12) == 6.5)
#   expect_error(add_postcode_vars("text"))
# })
```

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
